### 2018-07-18 writing/thesis/chapters/methods.tex
Setup latex template.
Add Euler and NS-Equations.
Further work on equation typesetting.

\chapter{Introduction}
Introduction here.

>>>>

\chapter{Methods}
Methods here.\todo{Organize into chapters!}

% TODO: Extract to settings.tex
\newcommand{\Qrho}{\ensuremath{\rho}}
\newcommand{\Qj}{\ensuremath{\rho \bm{v}}}
%\newcommand{\Qv}{\ensuremath{\Qrho^{-1} \Qj}}
\newcommand{\Qv}{\ensuremath{\bm{v}}}
\newcommand{\QE}{\ensuremath{\rho E}}
\newcommand{\stressT}{\ensuremath{\bm{\sigma}}}
\newcommand{\pressure}{\ensuremath{p}}
\newcommand{\maxConvEigen}{\ensuremath{\vert \lambda_c^{\text{max}} \vert}}
\newcommand{\maxViscEigen}{\ensuremath{\vert \lambda_v^{\text{max}} \vert}}

\section{Conservative Form}
Standard (hyperbolic) form of conservation law
\begin{equation}
  \label{eq:conservation-law}
 \frac{\partial}{\partial_t}  Q + \nabla \cdot F(Q) = S(\bm{x}, t, Q)
\end{equation}
extend to:
\begin{equation}
  \label{eq:conservation-law}
 \frac{\partial}{\partial_t}  Q + \nabla \cdot F(Q, \nabla Q) = S(\bm{x}, t, Q)
\end{equation}

\section{Compressible Euler}
Vector of conserved quantities:
\begin{equation}
  \label{eq:conserved-variables}
 Q = \left( \Qrho, \Qj, \QE \right) 
\end{equation}

\newcommand{\eulerFlux}{%
  \begin{pmatrix}
    \Qj \\
    \Qv  \otimes \Qj + \pressure \bm{I}  \\
    \Qv \cdot (\bm{I} \QE + \bm{I} \pressure)
  }
Flux:
\begin{equation}
  F(Q) = \eulerFlux
  \end{pmatrix}
\end{equation}
\begin{equation}
  \pressure = (\gamma - 1) \left(\QE - 0.5 \left(\Qv \cdot \Qj \right) \right)
\end{equation}

\section{Compressible Navier Stokes}
Following~\cite{dumbser2010arbitrary} by \citeauthor{dumbser2010arbitrary}.

Flux:
\begin{equation}
  F(Q, \nabla Q) = 
  \begin{pmatrix}
    \Qj \\
    \Qv  \otimes \Qj + \bm{I} \pressure + \stressT (Q, \nabla Q)  \\
    \Qv \cdot (\bm{I} \QE + \bm{I} \pressure + \stressT (Q, \nabla Q)) - \kappa \nabla T
  \end{pmatrix}
\end{equation}

With:
Pressure \pressure
\begin{equation}
  \pressure = (\gamma - 1) \left(\QE - 0.5 \left(\Qv \cdot \Qj \right) \right)
\end{equation}

Temperature $T$
\begin{equation}
 \frac{\pressure}{\Qrho} = RT
\end{equation}

Heat conduction coefficient $\kappa$
\begin{equation}
  \label{eq:heat-conduction-coeff}
  \kappa = \frac{\mu \gamma}{\Pr} \frac{1}{\gamma - 1} R
\end{equation}
with $R$ gas constant and $Pr$ Prandtl number

Sutherland's viscosity law:
\begin{equation}
  \label{eq:sutherland}
 \mu(T)  = \mu_0 {\left(\frac{T}{T_0}  \right)}^{\beta} \frac{T_0 + C}{T + C}
\end{equation}
with \(\beta = 1.5\), \(C = \text{const.}\), reference temperature $T_0$ and reference viscosity $\mu_=$.
Equal to
\begin{align}
  \lambda &= \frac{\mu_0 (T_0 + C)}{T_0^\beta} \\
  \mu(T) &= \lambda \frac{T^\beta}{T + C},
\end{align}
where $\lambda$ is constant for a given fluid.

stress tensor
\begin{equation}
  \label{eq:stress-tensor}
  \stressT(Q, \nabla Q) = \left(\nicefrac{2}{3} \mu \nabla \cdot \Qv \right) -
  \mu \left( \nabla (\Qv) + \nabla ( \Qv )^\intercal \right)
\end{equation}

Max eigenvalue of convective part \maxConvEigen\,i.e.\ of $\left( \partial \bm{F}/\partial \bm{Q}\right) \cdot \bm{n}$,
and viscous part \maxViscEigen\, i.e.\ of $\left( \partial \bm{F}/\partial \left( \nabla \bm{Q} \cdot \bm{n} \right)\right) \cdot \bm{n}$
is
\begin{align}
  \maxConvEigen \vert  &= \Vert \Qv \Vert + c\\
  \maxViscEigen \vert &= \max \left( \frac{4}{3} \frac{\mu}{\Qrho}
                                       , \frac{\gamma \mu}{\Pr \Qrho} \right)
\end{align}
with speed of sound $c = \sqrt{\gamma R T }$

Maximum timestep (\textsc{cfl})
\begin{equation}
 \Delta t = \frac{\text{CFL}}{2N + 1} \, \frac{h}{\maxConvEigen + 2 \maxViscEigen \frac{2N+1}{h}}
\end{equation}
with $N$ polynomial order and $h$ characteristic length scale of elements

Numerical flux:
\begin{equation}
  \label{eq:rusanov-flux}
  G(q_h^-, \nabla q_h^-; g_h^+, \nabla q_h^+) \cdot \bm{n} =
  \frac{1}{2} \left(
    F(q_h^+, \nabla q_h^+) +
    F(q_h^-, \nabla q_h^-)
  \right) -
  \frac{1}{2} s_\text{max} (q_h^+ - q_h^-)
\end{equation}
with
\begin{equation}
  \label{eq:parabolic-penalty}
  s_\text{max}  = \max \left(
\vert \lambda_c(q_h^-) \vert, \, \vert \lambda_c(q_h^+)
\right) +
2 \eta \max \left(
\vert \lambda_v(q_h^-) \vert, \, \vert \lambda_v(q_h^+)
\right)
\end{equation}
and
\begin{equation}
  \eta = \frac{N+1}{h}
\end{equation}
